Description of raw CFEC data processing for NCEAS portfolio effects working group

### 2016-03-25 process_raw_data/process_raw_cfec_data.Rmd
commit

```{r dataload, warnings=FALSE, message = FALSE}
load("cfec_w_IDs")
cfec = cfecnew
rm(cfecnew) # remove the old named object

# Remove A80 and CP vessels
A80<-c(68870,29923,22011,39798,59870,8500,41219,62545,56965,54693,1119,57228,69038,61081,61083,55921,57211,56964,36202,43260,54392,51873,48183,55767)
CP <-c(56987,59378,57621,59170,55767,57450,54886,56991,60407,60795,60202,60660,56789,56618,59503)
cfec <- filter(cfec,!adfg %in% c(A80,CP))
```

@@

```{r delColumns}
isNull = c("F_FG_MGT","C_CFACT", "F_DISTRC", "F_ERRFLG", "F_AYK", "G_FED_AR","F_BTAREA",
"A_CITY", "A_STATE", "A_ZIP", "P_YEAR", "I_NAME", "I_NAMTYP", "F_POT_DR", "F_PRCENT", 
"C_ADFGST", "F_CTDATE", "F_LNDATE", "F_NUMBER", "F_VALUE", "F_POUNDS", "F_TNUMB",  
"F_BATCH", "F_PERIOD",  "F_EMBSEQ", "F_PROCCK", "F_WEEK",  "F_TTYPE",    
"F_ITEM", "F_FSHERY",  "G_GEAR", "G_AREA", "G_PRC_AR",  "P_YEAR", "P_PMTSEQ", 
"p_check", "P_ID", "P_FEETYP", "P_ADFG", "P_FEEFLG", "P_FSHBLE", "F_DISPOS", 
"F_MPGMNM", "D_OPER", "D_O_FSHY", "D_O_PNUM", "D_O_PCHK", "D_O_YSEQ", "F_SIZE", 
"D_O_YCHK", "adfg")
cfec = cfec[,-which(names(cfec)%in%isNull)]
```

@@

cfec = cfec[-which(cfec$cadfg == ""), ]
cfec = cfec[-which(cfec$cadfg < 10000 | cfec$cadfg >= 98000), ]

@@

#------------------------------------------
# To add text species codes, load and join with Species lookup table
load("SpeciesTable.RData")

>>>>

```{r dataload, warnings=FALSE, message = FALSE}
load("Data/cfec_w_IDs.RData")
cfec = cfecnew
rm(cfecnew) # remove the old named object

#idx = grep("S 04T", cfec$p_fshy)
#group_by(cfec[idx,], year) %>% 
#  summarize(nSetnet = length(unique(p_holder)))
# Remove A80 and CP vessels
A80<-c(68870,29923,22011,39798,59870,8500,41219,62545,56965,54693,1119,57228,69038,61081,61083,55921,57211,56964,36202,43260,54392,51873,48183,55767)
CP <-c(56987,59378,57621,59170,55767,57450,54886,56991,60407,60795,60202,60660,56789,56618,59503)
cfec <- filter(cfec,!adfg %in% c(A80,CP))
rm(A80,CP)
```

@@

```{r delColumns}
isNull = c("F_FG_MGT","C_CFACT", "F_DISTRC", "F_ERRFLG", "F_AYK", "G_FED_AR","F_BTAREA",
"A_CITY", "A_STATE", "A_ZIP", "P_YEAR", "I_NAME", "I_NAMTYP", "F_POT_DR", "F_PRCENT", 
"C_ADFGST", "F_CTDATE", "F_LNDATE", "F_NUMBER", "F_VALUE", "F_POUNDS", "F_TNUMB",  
"F_BATCH", "F_PERIOD",  "F_EMBSEQ", "F_PROCCK", "F_WEEK",  "F_TTYPE",    
"F_ITEM", "F_FSHERY",  "G_GEAR", "G_AREA", "G_PRC_AR",  "P_YEAR", "P_PMTSEQ", 
"p_check", "P_ID", "P_FEETYP", "P_ADFG", "P_FEEFLG", "P_FSHBLE", "F_DISPOS", 
"F_MPGMNM", "D_OPER", "D_O_FSHY", "D_O_PNUM", "D_O_PCHK", "D_O_YSEQ", "F_SIZE", 
"D_O_YCHK", "adfg")
cfec = cfec[,-which(names(cfec)%in%isNull)]
rm(isNull)
```

@@

#cfec = cfec[-which(cfec$cadfg == ""), ]
#cfec = cfec[-which(cfec$cadfg < 10000 | cfec$cadfg >= 98000), ]

@@

#------------------------------------------
# To add text species codes, load and join with Species lookup table
load("Data/SpeciesTable.RData")
